PK object batch mode trial

### 2023-07-28 data-raw/batchMode_trial_gpm.Rmd
Updated plotting method interpolation

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                              "DTXSID5032600",
                                                              "DTXSID2021103"))
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9021924")

@@

# after fitting pk object for all cvt objects
# saveRDS(my_pk, file = "data-raw/all_cvt_pk.rds")
# saveRDS(my_pk, file = "data-raw/all_cvt_pk_JOINT.rds")
my_pk <- readRDS("data-raw/all_cvt_pk.rds")
my_AIC <- AIC(my_pk)
my_tkstats <- get_tkstats(my_pk)
my_IC <- left_join(AIC(my_pk), BIC(my_pk))

@@

all_my_data <- my_pk$data
all_my_data %>%
  group_by(Chemical,
           Species,
           Reference,
           Route,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc)) != n(),
         LOQ < Conc) %>%
  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc / meanConc) %>%
  count(foldConc > 2)
# 88.4% inside twofold
# 2.4%  above twofold
# 9.2%  below twofold

all_my_data %>%
  group_by(Chemical,
           Species,
           Reference,
           Route,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc)) != n(),
         LOQ < Conc) %>%
  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc / meanConc) %>%
  ggplot(aes(x = foldConc)) +
  geom_histogram(binwidth = 0.1,
                 fill = "grey5") +
  coord_cartesian(xlim =  c(0, 4),
                  ylim = c(0, 2000)) +
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0) +
  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
  annotate(geom= "text",
           x = 1.25, y = 1800,
           label = "88.4% of Observations\n within a factor of 2") +
  theme_classic() +
  labs(x = "Concentration Normalized to Average",
                y = "Number of Observations") +
  theme(panel.border = element_rect(color = "black", fill = NA),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))

@@

@@

my_preds %>%
  group_by(Chemical,
           Species,
           Route,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc_trans)) != n(),
         exclude == FALSE,
         Detect == TRUE) %>%
  mutate(meanConc = mean(Conc_trans, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc_trans / meanConc,
         foldPred = Conc_est / Conc_trans) %>% 
  # filter(model == "model_2comp") %>%
  mutate(VAR_DATA = ifelse(
    (foldPred > 2 | foldPred < 0.5) & (foldConc <= 2 & foldConc >= 0.5),
    TRUE, FALSE
  )) %>%
  filter(VAR_DATA == TRUE) %>%
  pull(VAR_DATA) %>% table()
  ggplot(aes(
    y = foldPred,
    x = foldConc
  )) +
  geom_bin2d(bins = 40, color = NA) +
  geom_hline(yintercept = c(0.5, 2), linetype = "dashed") +
  geom_vline(xintercept = c(0.5, 2), linetype = "dashed") +
  facet_grid(cols = vars(model)) +
  scale_x_log10(limits = c(0.0001, 50)) +
  scale_y_log10(limits = c(0.001, 1000)) +
  scale_fill_viridis_c(option = "cividis",
                       limits = c(1, 100),
                       oob = oob_squish) +
  labs(y = "Model Performance",
       x = "Data Variability") +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

@@

@@

>>>>

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
                subjects.species_harmonized %in% "hamster",
                studies.administration_route_normalized %in% "iv")
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9021924")

@@

# after fitting pk object for all cvt objects
# saveRDS(my_pk, file = "data-raw/all_cvt_pk.rds")
# saveRDS(my_pk, file = "data-raw/all_cvt_pk_JOINT.rds")
my_pk <- readRDS("data-raw/all_cvt_pk.rds")
my_coefs <- coef(my_pk, drop_sigma = FALSE)
get_winning_model(my_pk) %>%
  filter(model %in% c("model_2comp"),
         method == "L-BFGS-B") %>%
  dplyr::select(Chemical, Species) %>% distinct() %>% nrow()
all_my_data  %>% dplyr::select(Chemical, Species) %>% distinct() %>% nrow()
my_AIC <- AIC(my_pk)
my_tkstats <- get_tkstats(my_pk)
my_IC <- left_join(AIC(my_pk), BIC(my_pk))

@@

all_my_data <- my_pk$data
all_my_data %>%
  filter(Detect %in% TRUE,
         exclude %in% FALSE,
         Dose > 0) %>%
  group_by(Chemical,
           Species,
           Reference,
           Route, 
           Media,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc)) != n(),
         LOQ < Conc) %>%
  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc / meanConc) %>%
  filter(Route == "iv") %>%
  count(foldConc >= 0.5 & foldConc <= 2) %>%
  {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
# 88.9% inside twofold
# 2.2%  above twofold 
# 8.8%  below twofold
# 
#

all_my_data %>%
  filter(Detect %in% TRUE,
         exclude %in% FALSE,
         Dose > 0) %>%
  group_by(Chemical,
           Species,
           Reference,
           Route, 
           Media,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc)) != n(),
         LOQ < Conc) %>%
  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc / meanConc) %>%
  ggplot(aes(x = foldConc)) +
  geom_histogram(binwidth = 0.1,
                 fill = "grey5") +
  coord_cartesian(xlim =  c(0, 4),
                  ylim = c(0, 2000)) +
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0) +
  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
  # annotate(geom= "text",
  #          x = 1.25, y = 1800,
  #          label = "88.9% of Observations\n within a factor of 2") +
  theme_classic() +
  labs(x = "Concentration Normalized to Average",
                y = "Number of Observations") +
  theme(panel.border = element_rect(color = "black", fill = NA),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))

@@

winmodels <- AIC(my_pk) %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>%
  ungroup() %>%
  dplyr::select(Chemical, Species,
                method, model)

@@

my_preds %>%
  group_by(Chemical,
           Species,
           Route, Media,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc_trans)) != n(),
         model %in% c("model_flat"),
         exclude %in% FALSE,
         Detect %in% TRUE) %>%
  mutate(meanConc = mean(Conc_trans, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc_trans / meanConc,
         foldPred = Conc_est / Conc_trans) %>% 
  # For percentages
  ungroup() %>%
  count(!(foldPred >= 0.5 & foldPred <= 2) &
          !(foldConc >= 0.5 & foldConc <= 2)) %>%
  {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
  # For Plotting
  ggplot(aes(
    y = foldPred,
    x = foldConc
  )) +
  geom_bin2d(bins = 40, color = NA) +
  geom_hline(yintercept = c(0.5, 2), linetype = "dashed") +
  geom_vline(xintercept = c(0.5, 2), linetype = "dashed") +
  facet_grid(cols = vars(model)) +
  scale_x_log10(limits = c(0.0001, 50)) +
  scale_y_log10(limits = c(0.001, 1000)) +
  scale_fill_viridis_c(option = "cividis",
                       limits = c(1, 100),
                       oob = oob_squish) +
  labs(y = "Model Performance",
       x = "Data Variability") +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

@@

my_coefs %>% inner_join(get_winning_model(my_pk)) -> my_coefs
my_coefs %>% inner_join(get_data_summary(my_pk)) -> my_coefs

my_coefs %>%
  mutate(model = 
           case_when(
             model == "model_1comp" ~ "1-compartment",
             model == "model_2comp" ~ "2-compartment",
             model == "model_flat"  ~ "Null"
           )) %>%
  ggplot(aes(x = sigma_value/n_obs)) +
  geom_histogram(bins = 15,
                 color = NA, fill = "grey5") +
  scale_x_log10(labels = label_log()) +
  facet_grid(cols = vars(model)) +
  labs(x = "Size-normalized Sigma Value",
       y = "Number of Observations",
       title = "Distribution of Sigmas in CvTdb data") +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        plot.title = element_text(hjust = 0.5),
        axis.ticks = element_blank(),
        axis.line = element_blank())

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "NormalizedSigma_Distributions_2023-07.png"),
       height = 3, width = 5)
```

@@

```{r PredictionVariability_overtime}
my_pk <- readRDS("data-raw/all_cvt_pk.rds")
winmodels <- AIC(my_pk) %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>%
  ungroup() %>%
  dplyr::select(Chemical, Species,
                method, model)
my_preds <- inner_join(winmodels,
                       predict(my_pk,
                               use_scale_conc = TRUE))

my_tkstats <- inner_join(winmodels, get_tkstats(my_pk))
my_residuals <- residuals(my_pk, use_scale_conc = FALSE)

my_residuals %>%
  filter(exclude == FALSE) %>%
  inner_join(winmodels) %>%
  inner_join(my_tkstats %>%
              dplyr::select(Chemical, Species,
                            Route, Media,
                            tmax) %>%
              filter(!is.na(tmax))) %>%
  group_by(Chemical,
           Species,
           Route,
           Media,
           Dose) %>%
  mutate(
         normTime = ifelse(
           Route == "iv",
           1 + Time/max(Time),
           ifelse(
             Time > tmax,
             ((Time - tmax)/max(Time)) + 1,
             0.5 + Time/(2*tmax)
           )
         )) %>%
  distinct() %>%
  filter(Detect %in% TRUE) -> my_residuals2
my_residuals2 %>%
  # filter(Route == "oral") %>% View()
  ggplot(aes(
    x = normTime,
    y = Residuals
  )) +
  geom_point(alpha = 0.2, size = 0.5) +
  geom_point(data = filter(my_residuals2,
                           Chemical %in% "DTXSID4020533",
                           Species %in% "rat"),
             color = "orange2", size = 0.5) +
  geom_point(data = filter(my_residuals2,
                           Chemical %in% "DTXSID8031865",
                           Species %in% "rat"),
             color = "magenta4", size = 0.5) +
  geom_point(data = filter(my_residuals2,
                           Chemical %in% "DTXSID8025337",
                           Species %in% "rat"),
             color = "green2", size = 0.5) +
  geom_vline(xintercept = 1, color = "blue", linetype = "dashed") +
  geom_vline(xintercept = 2, color = "green4", linetype = "dashed") +
  facet_grid(cols = vars(Route),
             # rows = vars(model),
             scales = "free_x") +
  labs(x = "ADME-Normalized Time",
       y = "Winning Model Residuals") +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text.x = element_blank())

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "ADME_NormalizedTime-WinModelResiduals_onlyDetects_Highlighted_2023-07-19.png"),
       height = 4,
       width = 6,
       units = "in")
```

```{r log10_Pooled}
devtools::load_all()

my_log10pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) 
# Add Reference for Joint Analysis

my_log10pk <- do_preprocess(my_log10pk)

my_log10pk <- do_data_info(my_log10pk)

my_log10pk <- do_prefit(my_log10pk)

my_log10pk <- do_fit(my_log10pk)
# saveRDS(my_log10pk, file = "data-raw/all_cvt_pklog10.rds")

my_AIC <- AIC(my_log10pk)
my_tkstats <- get_tkstats(my_log10pk)

my_AIC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "bobyqa") %>%
  ungroup() %>%
  count(model)
# model_1comp 69
# model_2comp 35
# model_flat   7

my_AIC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>%
  ungroup() %>%
  count(model)
# model_1comp 77
# model_2comp 25
# model_flat   9

# To give summary RMSEs of Cmax and AUC...
my_eval <- eval_tkstats(my_log10pk) %>%
  group_by(method, model, .add = TRUE) %>%
  ungroup(Reference) %>%
  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
                                             na.rm = TRUE)^2)),
            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
                                          na.rm = TRUE)^2)),
            .groups = "keep")

my_eval %>%
  group_by(method) %>%
  summarize(AUC_meanRMSE = mean(AUC_inf_RMSE),
            AUC_mediRMSE = median(AUC_inf_RMSE),
            AUC_sdRMSE = sd(AUC_inf_RMSE),
            Cmax_meanRMSE = mean(Cmax_RMSE),
            Cmax_mediRMSE = median(Cmax_RMSE),
            Cmax_sdRMSE = sd(Cmax_RMSE)) %>% as.data.frame()

```{r log10_Joint}
my_log10pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

my_log10pk <- do_preprocess(my_log10pk)

my_log10pk <- do_data_info(my_log10pk)

my_log10pk <- do_prefit(my_log10pk)

my_log10pk <- do_fit(my_log10pk)

my_AIC <- AIC(my_log10pk)

my_AIC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "bobyqa") %>%
  ungroup() %>%
  count(model)
# model_1comp 56
# model_2comp 54
# model_flat  1

my_AIC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>%
  ungroup() %>%
  count(model)
# model_1comp 63
# model_2comp 48
# model_flat  0

my_eval <- eval_tkstats(my_log10pk)

my_eval %>%
  group_by(method) %>%
  summarize(AUC_meanRMSE = mean(AUC_inf_RMSE),
            AUC_mediRMSE = median(AUC_inf_RMSE),
            AUC_sdRMSE = sd(AUC_inf_RMSE),
            Cmax_meanRMSE = mean(Cmax_RMSE),
            Cmax_mediRMSE = median(Cmax_RMSE),
            Cmax_sdRMSE = sd(Cmax_RMSE)) %>%
  as.data.frame()

```{r boilerplate_RMSE_analysis}
my_pk <- readRDS("data-raw/all_cvt_pk.rds")
my_AIC <- AIC(my_pk)

my_AIC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "bobyqa") %>%
  ungroup() %>%
  count(model)

my_AIC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>%
  ungroup() %>%
  count(model)

my_eval <- eval_tkstats(my_pk)

my_eval %>%
  group_by(method) %>%
  summarize(AUC_meanRMSE = mean(AUC_inf_RMSE),
            AUC_mediRMSE = median(AUC_inf_RMSE),
            AUC_sdRMSE = sd(AUC_inf_RMSE),
            Cmax_meanRMSE = mean(Cmax_RMSE),
            Cmax_mediRMSE = median(Cmax_RMSE),
            Cmax_sdRMSE = sd(Cmax_RMSE)) %>%
  as.data.frame()
```

```{r bad_fits}
predata_chemical <- my_pk$prefit$fit_check %>%
  filter(fit_decision == "abort") %>%
  pull(Chemical) %>%
  unique()

my_pk <- pk(data = cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% predata_chemical)) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) 
# Add Reference for Joint Analysis

get_data(my_pk) %>% View()

plot(my_pk, print_out = TRUE)[[1]] +
  labs(subtitle = "Dibutyl phthalate (DBP)") +
  theme(aspect.ratio = 1,
        plot.subtitle = element_text(hjust = 0.5))
ggsave(paste0(Sys.getenv("FIG_DIR"),
              "DTXSID20211781_rat_badFit.png"),
       width = 6,
       height = 4,
       units = "in")

my_pk <- pk(data = cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID2021315")) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

plot(my_pk,
     method = "L-BFGS-B",
     n_interp = 10,
     print_out = TRUE)[[1]] +
  labs(subtitle = "2,3,7,8-tetrachlorodibenzo-p-dioxin") +
  scale_x_continuous(breaks = c(0, (1:4)*(24*7*4)),
                     labels = c(0, 1:4),
                     name = "Time (months)") +
  guides(color = "none",
         shape = "none") +
  theme(aspect.ratio = 1,
        plot.subtitle = element_text(hjust = 0.5))
ggsave(paste0(Sys.getenv("FIG_DIR"),
              "DTXSID2021315_rat_badFit.png"),
       width = 8,
       height = 5,
       units = "in")

my_pk <- pk(data = cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

plot(my_pk,
     method = "L-BFGS-B",
     use_scale_conc = FALSE,
     log10_C = FALSE,
     n_interp = 50,
     print_out = TRUE)[[1]] +
  labs(subtitle = "3,3',4,4',5-pentachlorobiphenyl (without Dose-Normalized Fit)") +
  scale_x_continuous(breaks = c(0, (1:14)*(24*7*4)),
                     labels = c(0, 1:14),
                     name = "Time (months)") +
  guides(color = "none",
         shape = "none") +
  theme(aspect.ratio = 1,
        plot.subtitle = element_text(hjust = 0.5))
ggsave(paste0(Sys.getenv("FIG_DIR"),
              "DTXSID3032179_rat_badFit_noDoseNorm.png"),
       width = 7.5,
       height = 5,
       units = "in")

my_pk <- pk(data = cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

plot(my_pk,
     method = "L-BFGS-B",
     use_scale_conc = FALSE,
     log10_C = FALSE,
     n_interp = 50,
     print_out = TRUE)[[1]] +
  labs(subtitle = "3,3',4,4',5-pentachlorobiphenyl (Dose-Normalized Fit)") +
  scale_x_continuous(breaks = c(0, (1:14)*(24*7*4)),
                     labels = c(0, 1:14),
                     name = "Time (months)") +
  guides(color = "none",
         shape = "none") +
  theme(aspect.ratio = 1,
        plot.subtitle = element_text(hjust = 0.5))
ggsave(paste0(Sys.getenv("FIG_DIR"),
              "DTXSID3032179_rat_badFit_DoseNorm.png"),
       width = 7.5,
       height = 5,
       units = "in")

my_pk <- pk(data = cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID1034187")) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

get_data(my_pk) %>% View()
plot(my_pk,
     method = "L-BFGS-B",
     use_scale_conc = TRUE,
     log10_C = FALSE,
     n_interp = 100,
     print_out = TRUE)[[1]] +
  labs(subtitle = "Tamoxifen") +
  theme(aspect.ratio = 1,
        plot.subtitle = element_text(hjust = 0.5))
ggsave(paste0(Sys.getenv("FIG_DIR"),
              "DTXSID1034187_rat_badFit_.png"),
       width = 7,
       height = 7,
       units = "in")
# Fit is actually ok, but there are lot's of non-Detects in the data
# There are many doses that are fully non-Detects.

problem_dose <- all_my_data %>%
  group_by(Chemical, Species, Route, Media, Dose) %>%
  filter(sum(Detect) == 0) %>%
  dplyr::select(Chemical, Species, Route, Media, Dose) %>%
  rename(chemicals_analyzed.dsstox_substance_id = Chemical,
         subjects.species_harmonized = Species,
         series.conc_medium_normalized = Media,
         studies.administration_route_normalized = Route,
         studies.dose_level_normalized_corrected = Dose) %>%
  distinct()

problem_dose_DTX <- all_my_data %>%
  group_by(Chemical, Species, Route, Media, Dose) %>%
  filter(sum(Detect) == 0) %>%
  ungroup() %>%
  pull(1) %>% unique()

# Figure out if the fits improve if we exclude Dose groups that do not have
# any Detects

my_pk_full <- pk(data = cvt %>%
                   dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% 
                                   "DTXSID1034187")) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species))

my_pk_full <- do_preprocess(my_pk_full)
my_pk_full <- do_fit(my_pk_full)

plot(my_pk_full,
     n_interp = 50,
     use_scale_conc = TRUE,
     print_out = TRUE)

my_pk_trimmed <- pk(data = cvt %>%
                      dplyr::filter(chemicals_analyzed.dsstox_substance_id %in%
                                      "DTXSID1034187") %>%
                      anti_join(problem_dose)) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species))

my_pk_trimmed <- do_preprocess(my_pk_trimmed)
my_pk_trimmed <- do_fit(my_pk_trimmed)

AIC(my_pk_full) %>% View("full")
AIC(my_pk_trimmed) %>% View("trimmed")

get_winning_model(my_pk_full)
get_winning_model(my_pk_trimmed)

eval_tkstats(my_pk_full) %>% View("full_tkstats")
eval_tkstats(my_pk_trimmed) %>% View("trimmed_tkstats")
get_tkstats(my_pk_trimmed) %>% View()

plot(my_pk_trimmed,
     n_interp = 50,
     method = "L-BFGS-B",
     print_out = TRUE)
